---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# Overview
ReCoNet provides methods for:

- network connectivity comparison
- permutation-based statistical inference
- projection-based network replication

The package operates directly on precontructed adjacency matrices.

## Installation 

```{r, eval=FALSE}
devtools::install_github("thaovu1/ReCoNet")

```

## Load package 

```{r setup}
library(ReCoNet)
```

## Simulated Example Data

```{r}
set.seed(123)

A <- matrix(runif(100, 0, 1), 10, 10)
B <- matrix(rnorm(100, 0, 1), 10, 10)

```

## Network Comparison

The compare_networks() function evaluates total connectivity differences between two networks.

### Sign-flipping permutation

```{r}
res_sf <- compare_networks(
  A = A,
  B = B,
  method = "sign_flipping",
  p = 5,
  n_perm = 1000
)

res_sf$p_value
```

The sign-flipping framework evaluates whether the signed connectivity differences deviate from the null expectation of random sign assignment.


### Node relabeling permutation

```{r}
res_rl <- compare_networks(
  A = A,
  B = B,
  method = "relabeling",
  statistic = "PND",
  p = 6,
  n_perm = 1000
)

res_rl$p_value

```

## Network Replication

The bootstrap_projection() function evaluates projection-based replication in an independent dataset.

```{r}
n <- 50
p <- 10

X1 <- matrix(rnorm(n * p), n, p)
X2 <- matrix(rnorm(n * p), n, p)

Y1 <- matrix(rnorm(n), n,1)
Y2 <- matrix(rnorm(n), n,1)
```

### Inference of Replication with bootstrap

```{r}
proj_res <- bootstrap_projection(
  B = 500,
  M = A,
  X1 = X1,
  Y1 = Y1,
  X2 = X2,
  Y2 = Y2,
  npc = 3,
  alpha = 0.05
)

proj_res
```

## Interpretation

The network comparison framework assesses global connectivity differences between two networks using permutation-based significance testing.

The replication framework evaluates reproducibility of network-derived latent structure in independent datasets.

## Session Information

```{r}
sessionInfo()
```
